### 2023-01-11 output/summary_statistics/tables/summary_statistics.tex
Added commas to numbers in summary statistics table

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
 & Foreclosure & 0.02 & 0.14 & 40,727 \\
 & No cause & 0.11 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
 & Transferred from other court & 0.05 & 0.22 & 40,727 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
 & Case duration & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.23 & 40,727 \\
 & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
 & Case mediated & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 1890.34 & 5279.49 & 40,727 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2471065.61 & 6218383.08 & 36,587 \\
 & Land value & 112575.80 & 659661.29 & 36,587 \\
 & Other value & 10900678.30 & 26482630.60 & 36,587 \\
 & Total property value & 8350204.19 & 22073916.94 & 36,587 \\
 & Units & 40.76 & 157.57 & 36,587 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50658.53 & 26562.19 & 35,058 \\
 & Median two bedroom rent (2015) & 1063.30 & 352.38 & 26,191 \\
 & Population density (2010) & 9309.47 & 9457.90 & 35,058 \\
 & Portion white (2010) & 0.56 & 0.30 & 35,058 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377384.02 & 316645.29 & 10,096 \\
 & Five years before filing date & 261462.86 & 238040.64 & 9,842 \\
 & Four years before filing date & 280243.32 & 276051.45 & 9,968 \\
 & One year after filing date & 421601.75 & 344328.86 & 10,443 \\
 & One year before filing date & 351172.05 & 311982.74 & 10,190 \\
 & Three years after filing date & 501611.80 & 780467.01 & 5,894 \\
 & Three years before filing date & 307137.16 & 369763.53 & 10,172 \\
 & Two years after filing date & 477948.08 & 457694.83 & 9,175 \\
 & Two years before filing date & 341084.08 & 987145.51 & 10,182 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 40,727 \\
 & Foreclosure & 0.02 & 0.14 & 40,727 \\
 & No cause & 0.11 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 0.43 & 40,727 \\
 & Transferred from other court & 0.05 & 0.22 & 40,727 \\
\cline{1-5}
\multirow[c]{6}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 40,727 \\
 & Case duration & 57.81 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.23 & 40,727 \\
 & Case involuntarily dismissed & 0.29 & 0.45 & 40,727 \\
 & Case mediated & 0.41 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 5,279.49 & 40,727 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 0.46 & 40,727 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 2,471,065.61 & 6,218,383.08 & 36,587 \\
 & Land value & 112,575.80 & 659,661.29 & 36,587 \\
 & Other value & 10,900,678.30 & 26,482,630.60 & 36,587 \\
 & Total property value & 8,350,204.19 & 22,073,916.94 & 36,587 \\
 & Units & 40.76 & 157.57 & 36,587 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 50,658.53 & 26,562.19 & 35,058 \\
 & Median two bedroom rent (2015) & 1,063.30 & 352.38 & 26,191 \\
 & Population density (2010) & 9,309.47 & 9,457.90 & 35,058 \\
 & Portion white (2010) & 0.56 & 0.30 & 35,058 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel F: Zestimates Around Filing Date}} & Filing date & 377,384.02 & 316,645.29 & 10,096 \\
 & Five years before filing date & 261,462.86 & 238,040.64 & 9,842 \\
 & Four years before filing date & 280,243.32 & 276,051.45 & 9,968 \\
 & One year after filing date & 421,601.75 & 344,328.86 & 10,443 \\
 & One year before filing date & 351,172.05 & 311,982.74 & 10,190 \\
 & Three years after filing date & 501,611.80 & 780,467.01 & 5,894 \\
 & Three years before filing date & 307,137.16 & 369,763.53 & 10,172 \\
 & Two years after filing date & 477,948.08 & 457,694.83 & 9,175 \\
 & Two years before filing date & 341,084.08 & 987,145.51 & 10,182 \\
\cline{1-5}
\bottomrule
\end{tabular}
